---
title: "Confidence Intervals for Means"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Confidence Intervals for Means}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(statpsych)) {remotes::install_github("dbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Confidence Intervals for Means

This vignette compares the use of `statpsych` and `spTools` functions to compute confidence intervals for means and differences between means. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Confidence Intervals for a Set of Means

Compare separate `statpsych` calls with one vectorized `spTools` call.

```{r}
# statpsych version
ci.mean(alpha = .05, m = 5.2, sd = 1.1, n = 30)
ci.mean(alpha = .05, m = 6.1, sd = 1.3, n = 28)

# spTools version
ci.mean.vec(alpha = .05, m = c(5.2, 6.1), sd = c(1.1, 1.3), n = c(30, 28))
```

### Confidence Interval for Independent Groups Mean Difference

Compare independent-group mean difference output between packages.

```{r}
# statpsych version
ci.mean2(alpha = .05, m1 = 15.4, m2 = 10.3, sd1 = 2.67, sd2 = 2.15, n1 = 30, n2 = 20)

# spTools version
ci.mean2.vec(alpha = .05, m = c(15.4, 10.3), sd = c(2.67, 2.15), n = c(30, 20))
```

Compare standardized mean difference output for independent groups.

```{r}
# statpsych version
ci.stdmean2(alpha = .05, m1 = 35.1, m2 = 26.7, sd1 = 7.32, sd2 = 6.98, n1 = 30, n2 = 30)

# spTools version
ci.stdmean2.vec(alpha = .05, m = c(35.1, 26.7), sd = c(7.32, 6.98), n = c(30, 30))
```

### Confidence Interval for Paired Samples Mean Difference

Compare paired-sample mean difference output between packages.

```{r}
# statpsych version
ci.mean.ps(alpha = .05, m1 = 58.2, m2 = 51.4, sd1 = 7.43, sd2 = 8.92, cor = .537, n = 30)

# spTools version
ci.mean.ps.vec(alpha = .05, m = c(58.2, 51.4), sd = c(7.43, 8.92), cor = .537, n = 30)
```

Compare standardized paired-sample effect size output.

```{r}
# statpsych version
ci.stdmean.ps(alpha = .05, m1 = 110.4, m2 = 102.1, sd1 = 15.3, sd2 = 14.6, cor = .75, n = 25)

# spTools version
ci.stdmean.ps.vec(alpha = .05, m = c(110.4, 102.1), sd = c(15.3, 14.6), cor = .75, n = 25)
```
