---
title: "Confidence Intervals for Correlation Comparisons"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Confidence Intervals for Correlation Comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(statpsych)) {remotes::install_github("dbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Confidence Intervals for Correlation Comparisons

This vignette compares the use of `statpsych` and `spTools` functions to compute confidence intervals for correlation comparisons. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Independent Group Correlation Comparisons

Use `statpsych` functions to build group and comparison rows manually.

```{r}
ci.cor.vec(alpha = .05, cor = c(.64, .31), s = c(0, 0), n = c(200, 200)) -> groups
ci.cor2.vec(alpha = .05, cor = c(.64, .31), n = c(200, 200))[1, c("Estimate", "SE", "LL", "UL")] -> compare
results <- rbind(groups, compare)
rownames(results) <- c("Group 1", "Group 2", "Comparison")
results
```

Or use the `spTools` helper function to produce the same independent-group comparison table.

```{r}
ci.cor.compare(
  alpha = .05,
  cor = c(.64, .31),
  s = c(0, 0),
  n = c(200, 200)
)
```

### Dependent Correlation Comparisons

Use `statpsych` functions to build measure and comparison rows manually for the dependent-correlation case.

```{r}
ci.cor.vec(alpha = .05, cor = c(.396, .179), s = c(0, 0), n = c(166, 166)) -> groups
ci.cor.dep.vec(alpha = .05, cor = c(.396, .179), cor12 = .088, n = 166)[1, c("Estimate", "SE", "LL", "UL")] -> compare
results <- rbind(groups, compare)
rownames(results) <- c("Measure 1", "Measure 2", "Comparison")
results
```

Or use the `spTools` helper function to produce the same dependent-correlation comparison table.

```{r}
ci.cor.dep.compare(
  alpha = .05,
  cor = c(.396, .179),
  cor12 = .088,
  n = 166,
  s = 0
)
```
