---
title: "Confidence Intervals for Proportion Comparisons"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Confidence Intervals for Proportion Comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(statpsych)) {remotes::install_github("dbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Confidence Intervals for Proportion Comparisons

This vignette compares the use of `statpsych` and `spTools` functions to compute confidence intervals for proportion comparisons. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Independent Group Proportion Comparisons

Use `statpsych` functions to build group and comparison rows manually for the proportion difference.

```{r}
ci.prop.vec(alpha = .05, f = c(57, 15), n = c(100, 100)) -> groups
ci.prop2.vec(alpha = .05, f = c(57, 15), n = c(100, 100))[1, c("Estimate", "SE", "LL", "UL")] -> compare
results <- rbind(groups, compare)
rownames(results) <- c("Group 1", "Group 2", "Difference")
results
```

Or use the `spTools` helper function to produce the same difference table.

```{r}
ci.prop.compare(
  alpha = .05,
  f = c(57, 15),
  n = c(100, 100)
)
```

### Paired Proportion Comparisons

Use `statpsych` functions to build measure and comparison rows manually for paired proportions.

```{r}
f00 <- 12
f01 <- 4
f10 <- 26
f11 <- 6

n <- f00 + f01 + f10 + f11
f <- c(f10 + f11, f01 + f11)

ci.prop.vec(alpha = .05, f = f, n = c(n, n)) -> groups
ci.prop.ps(alpha = .05, f00 = f00, f01 = f01, f10 = f10, f11 = f11)[1, c("Estimate", "SE", "LL", "UL")] -> compare
results <- rbind(groups, compare)
rownames(results) <- c("Measure 1", "Measure 2", "Comparison")
results
```

Or use the `spTools` helper function to produce the same paired-proportion comparison table.

```{r}
results <- ci.prop.ps.compare(
  alpha = .05,
  f00 = 12,
  f01 = 4,
  f10 = 26,
  f11 = 6
)
results
```
