---
title: "Confidence Intervals for Mean Comparisons"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Confidence Intervals for Mean Comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(statpsych)) {remotes::install_github("dbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Confidence Intervals for Mean Comparisons

This vignette compares the use of `statpsych` and `spTools` functions to compute confidence intervals for mean comparisons. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Independent Group Mean Comparisons

Use `statpsych` functions to build group and comparison rows manually.

```{r}
ci.mean.vec(alpha = .05, m = c(5.2, 6.1), sd = c(1.1, 1.3), n = c(30, 28)) -> groups
ci.mean2.vec(alpha = .05, m = c(6.1, 5.2), sd = c(1.3, 1.1), n = c(28, 30))[1, c(1, 2, 4, 6, 7)] -> compare
results <- rbind(groups,compare)
rownames(results) <- c("Group 1", "Group 2", "Comparison")
results
```

Or use the `spTools` helper function to produce the same independent-group comparison table.

```{r}
ci.mean2.compare(
  alpha = .05,
  m = c(5.2, 6.1),
  sd = c(1.1, 1.3),
  n = c(30, 28)
)
```

### Paired Samples Mean Comparisons

Use `statpsych` functions to build paired-sample group and comparison rows manually.

```{r}
ci.mean.vec(alpha = .05, m = c(58.2, 51.4), sd = c(7.43, 8.92), n = c(30, 30)) -> groups
ci.mean.ps.vec(alpha = .05, m = c(58.2, 51.4), sd = c(7.43, 8.92), cor = .537, n = 30)[1, c(1, 2, 4, 6, 7)] -> compare
results <- rbind(groups, compare)
rownames(results) <- c("Measure 1", "Measure 2", "Comparison")
results
```

Or use the `spTools` helper function to produce the same paired-sample comparison table.

```{r}
ci.mean.ps.compare(
  alpha = .05,
  m = c(58.2, 51.4),
  sd = c(7.43, 8.92),
  cor = .537,
  n = 30
)
```

### Between-Subjects Mean Contrasts

Use `statpsych` functions to build two contrasts and their difference manually for independent groups. The first contrast is the grand mean; the second identifies Level 1 specifically. Their difference captures how Level 1 deviates from the grand mean.

```{r}
q1 <- c(1/3, 1/3, 1/3)
q2 <- c(1, 0, 0)
ci.lc.mean.bs(alpha = .05, m = c(8, 11, 12), sd = c(1.414, 2.211, 2.449), n = c(10, 10, 10), v = q1)[1, c("Estimate", "SE", "df", "LL", "UL")] -> c1
ci.lc.mean.bs(alpha = .05, m = c(8, 11, 12), sd = c(1.414, 2.211, 2.449), n = c(10, 10, 10), v = q2)[1, c("Estimate", "SE", "df", "LL", "UL")] -> c2
ci.lc.mean.bs(alpha = .05, m = c(8, 11, 12), sd = c(1.414, 2.211, 2.449), n = c(10, 10, 10), v = q2 - q1)[1, c("Estimate", "SE", "df", "LL", "UL")] -> diff
results <- rbind(c1, c2, diff)
rownames(results) <- c("Grand Mean", "L1 Only", "Difference")
results
```

Or use the `spTools` helper function to produce the same between-subjects complex contrast table.

```{r}
ci.lc.mean.bs.complex(
  alpha = .05,
  m = c(8, 11, 12),
  sd = c(1.414, 2.211, 2.449),
  n = c(10, 10, 10),
  q1 = c(1/3, 1/3, 1/3),
  q2 = c(1, 0, 0),
  labels = c("Grand Mean", "L1 Only")
)
```

### Within-Subjects Mean Contrasts

Use `statpsych` functions to build two contrasts and their difference manually for repeated measures. The first contrast is the grand mean; the second identifies Level 1 specifically. Their difference captures how Level 1 deviates from the grand mean.

```{r}
R <- matrix(c(1, .7, .7, .7, 1, .7, .7, .7, 1), 3, 3)
q1 <- c(1/3, 1/3, 1/3)
q2 <- c(1, 0, 0)
ci.lc.mean.ws(alpha = .05, m = c(8, 11, 12), s = c(1.414, 2.211, 2.449), R = R, n = 10, q = q1) -> c1
ci.lc.mean.ws(alpha = .05, m = c(8, 11, 12), s = c(1.414, 2.211, 2.449), R = R, n = 10, q = q2) -> c2
ci.lc.mean.ws(alpha = .05, m = c(8, 11, 12), s = c(1.414, 2.211, 2.449), R = R, n = 10, q = q2 - q1) -> diff
results <- rbind(c1, c2, diff)
rownames(results) <- c("Grand Mean", "L1 Only", "Difference")
results
```

Or use the `spTools` helper function to produce the same within-subjects complex contrast table.

```{r}
ci.lc.mean.ws.complex(
  alpha = .05,
  m = c(8, 11, 12),
  s = c(1.414, 2.211, 2.449),
  R = matrix(c(1, .7, .7, .7, 1, .7, .7, .7, 1), 3, 3),
  n = 10,
  q1 = c(1/3, 1/3, 1/3),
  q2 = c(1, 0, 0),
  labels = c("Grand Mean", "L1 Only")
)
```
