---
title: "Confidence Intervals for Proportions"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Confidence Intervals for Proportions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(statpsych)) {remotes::install_github("dbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Confidence Intervals for Proportions

This vignette compares the use of `statpsych` and `spTools` functions to compute confidence intervals for proportions and differences between proportions. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Confidence Intervals for a Set of One-Sample Proportions

Compare separate `statpsych` calls with one vectorized `spTools` call.

```{r}
# statpsych version
ci.prop(alpha = .05, f = 120, n = 300)
ci.prop(alpha = .05, f = 95, n = 250)

# spTools version
ci.prop.vec(alpha = .05, f = c(120, 95), n = c(300, 250))
```

### Confidence Interval for Independent Groups Proportion Difference

Compare independent-groups proportion difference output between packages.

```{r}
# statpsych version
ci.prop2(alpha = .05, f1 = 57, f2 = 15, n1 = 100, n2 = 100)

# spTools version
ci.prop2.vec(alpha = .05, f = c(57, 15), n = c(100, 100))
```
